### 2020-08-18 thesis/chap_1.tex
updates

Ecological connectivity, defined as the extent to which the landscape supports the movements of organisms, can be strongly affected by land use. It is an important component of the resilience of populations in heterogeneous and fragmented landscapes. Land use changes such as urban sprawl and agricultural intensification intensify habitat fragmentation and landscape homogenization, leading to the erosion of ecological connectivity. The Montérégie region in southern Quebec, where this work takes place, is experiencing urban growth and sprawl. We present a framework that integrates land-use, climate change and connectivity modeling to forecast future changes in connectivity, using a combination of statistical modeling, MCMC-based simulations, and circuit theory. We used a hybrid modeling approach to project future land use changes using different climate scenarios, and estimate future changes in functional connectivity flow for 5 different umbrella species. We explore the flexibility of a scenario approach in forecasting the range of possible futures for ecological connectivity in the region, derive insights for the hypothetical design of a local network of connected protected areas resilient to future landscape change. In conclusion, we highlight the need for a multi stakeholder approach in the definition of scenarios and conservation priorities.\\

@@

% [back to what we want to do]
Climate change can interact with land use change in ways that impact biodiversity \citep{oliver_interactions_2014} It is therefore likely that connectivity models integrating these two drivers would improve connectivity conservation methods such as CPAN design. Yet, in a recent review, \cite{costanza_landscape_2019} have found that connectivity methodological frameworks rarely combine  land use change and climate change. Here, we build on recent connectivity modelling work using circuit theory, by pairing it with a hybrid land use and climate change model \citep{albert_applying_2017}. The model we develop uses a combination of statistical modelling and simulations based on a Markov Chain Monte Carlo (MCMC) method, combining Random forests (RF) models with a Cellular automaton (CA) model. We use this RF-CA model to project future land use changes and estimate the changes in potential functional connectivity for five different umbrella species, under different climate change scenarios. We also derive conservation insights for the design of a hypothetical regional network of connected protected areas resilient to future landscape change. In addition, we provide an analysis of past land use change trends in our study region, the Monteregie region in southern Quebec.

>>>>

Ecological connectivity, defined as the extent to which the landscape supports the movements of organisms, can be strongly affected by land use. It is an important component of the resilience of populations in heterogeneous and fragmented landscapes. Land use changes such as urban sprawl and agricultural intensification intensify habitat fragmentation and landscape homogenization, leading to the erosion of ecological connectivity. The Montérégie region in southern Quebec, where this work takes place, is experiencing urban growth and sprawl. We present a framework that integrates land-use, climate change and connectivity modeling to forecast future changes in connectivity, using a combination of statistical modeling, MCMC-based simulations, and circuit theory. We used a hybrid modeling approach to project future land use changes using different climate scenarios, and estimate future changes in functional connectivity flow for 5 different umbrella species. We explore the flexibility of a scenario approach in forecasting the range of possible futures for ecological connectivity in the region, derive potential insights for the hypothetical design of a local network of connected protected areas resilient to future landscape change. In conclusion, we highlight the need for a multi stakeholder approach in the definition of scenarios and conservation priorities.\\

@@

% [back to what we want to do]
Climate change can interact with land use change in ways that impact biodiversity \citep{oliver_interactions_2014} It is therefore likely that connectivity models integrating these two drivers would improve connectivity conservation methods such as CPAN design. Yet, in a recent review, \cite{costanza_landscape_2019} have found that connectivity methodological frameworks rarely combine  land use change and climate change. Here, we build on recent connectivity modelling work using circuit theory, by pairing it with a hybrid land use and climate change model \citep{albert_applying_2017}. The model we develop uses a combination of statistical modelling and simulations based on a Markov Chain Monte Carlo (MCMC) method, combining Random forests (RF) models with a Cellular automaton (CA) model. We use this RF-CA model to project future land use changes and estimate the changes in potential functional connectivity for five different umbrella species, under different climate change scenarios. We also derive potential insights for the design of a hypothetical regional network of connected protected areas resilient to future landscape change. In addition, we provide an analysis of past land use change trends in our study region, the Monteregie region in southern Quebec.

### 2020-08-18 thesis/chap_2.tex
re captions
updates

Connectivity conservation science, whose goal is to preserve the continuity of habitat throughout a given landscape, proceeds by identifying priority areas given the current configuration of the landscape. However, current connectivity conservation planning methods often do not confront the results of the prioritization with the priorities perceived by stakeholders. There is a need for planning tools to allow for this confrontation to happen. The Montérégie region in southern Quebec, where this work takes place, is experiencing urban growth and sprawl, and stakeholders show an increasing interest in connectivity conservation tools. Those tools need to be able to guide stakeholders through an iterative process of conservation and land use scenario building. We take a first step toward deriving the basis for such community-driven scenarios and tools by presenting the results of a community workshop organized between multiple stakeholders in Montérégie. We use those results to derive simple land use change scenarios and use those scenarios to constrain the integrated model previously derived. We discuss the importance of considering stakeholder inputs to produce a resilient network of protected areas and highlight the need for a multi- stakeholder approach in the definition of conservation priorities. \\

@@

% Linear
\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/surf_chap2.png}
}
 \caption{Change in the number of features (in \% of the the 2010 flow) identified by the SURF analyssis between 2010 (observed) and 2100 (predicted), contrasting BAU scenario with other conservation scenarios - linear graph.}
 \label{fig:surf_linear_2}
\end{figure}

% Radar
\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/surf_radar_chap2.png}
}
 \caption{Change in the number of features (in \% of the the 2010 flow) identified by the SURF analyssis between 2010 (observed) and 2100 (predicted), contrasting BAU scenario with other conservation scenarios - radar graph.}
 \label{fig:surf_radar_2}
\end{figure}

>>>>

Connectivity conservation science, whose goal is to preserve the continuity of habitat throughout a given landscape, proceeds by identifying priority areas given the current configuration of the landscape. However, current connectivity conservation planning methods often do not confront the results of the prioritization with the priorities perceived by stakeholders. There is a need for planning tools to allow for this confrontation to happen. The Montérégie region in southern Quebec, where this work takes place, is experiencing urban growth and sprawl, and stakeholders show an increasing interest in connectivity conservation tools. Those tools need to be able to guide stakeholders through an iterative process of conservation and land use scenario building. We take a first step toward deriving the basis for such community-driven scenarios and tools by presenting the results of a community workshop organized between multiple stakeholders in Montérégie. We use those results to derive simple land use change scenarios and use those scenarios to constrain the integrated model previously derived. We discuss the importance of considering stakeholder inputs to produce a resilient network of protected areas and highlight the need for a multi-stakeholder approach in the definition of conservation priorities. \\

@@

% Linear
\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/surf_chap2.png}
}
 \caption{Change in the number of features (in \% of the the 2010 flow) identified by the SURF analyssis between 2010 (observed) and 2100 (predicted), contrasting BAU scenario with other conservation scenarios - linear graph.}
 \label{fig:surf_linear_2}
\end{figure}

% Radar
\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/surf_radar_chap2.png}
}
 \caption{Change in the number of features (in \% of the the 2010 flow) identified by the SURF analyssis between 2010 (observed) and 2100 (predicted), contrasting BAU scenario with other conservation scenarios - radar graph.}
 \label{fig:surf_radar_2}
\end{figure}

### 2020-08-18 thesis/thesis.tex
updates

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%         English Abstract                        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SetAbstractEnName{{Abstract}}%
\SetAbstractEnText{Connectivity conservation science, whose goal is to preserve the continuity of habitat throughout a given landscape, proceeds by identifying priority areas given the current configuration of the landscape. However, current connectivity conservation planning methods often do not take into account risks associated with future land use change, and might not go as far as to confront the results of the prioritization with the priorities perceived by stakeholders. In this thesis, we attempted to remedy those two issues in an ongoing effort of connectivity conservation planning for the region of Montérégie in Southern Quebec, Canada. In the first chapter, we built on past work of connectivity modelling using circuit theory in the region and complemented it with land use and climate change modelling that uses a combination of statistical modelling and MCMC-based simulations. Models trained on past land use data were used to project future land use changes and estimate future changes in potential functional connectivity for 5 different umbrella species. In a second chapter, we compare those results with the perceived conservation priorities in the region. We conducted a day-long workshop with stakeholders involved in the ongoing connectivity conservation planning effort in the region and collected information on landscape features considered “core” and “linkages” priority areas. We showed the importance of considering land use changes to produce a resilient network of protected areas and highlight the need for a multi- stakeholder approach in the definition of conservation scenarios and the identification of regional priorities.}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%         English Abstract                        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SetAbstractEnName{{Abstract}}%
\SetAbstractEnText{Connectivity conservation science, whose goal is to preserve the continuity of habitat throughout a given landscape, proceeds by identifying priority areas given the current configuration of the landscape. However, current connectivity conservation planning methods often do not take into account risks associated with future land use and climate change, and often do not confront the results of the prioritization with the priorities perceived by stakeholders. In this thesis, we attempted to remedy those two issues in the context of an ongoing effort of connectivity conservation planning for the region of Montérégie in Southern Quebec, Canada. In the first chapter, we built on past work of connectivity modelling using circuit theory in the region and complemented it with land use and climate change modelling that uses a combination of statistical modelling and MCMC-based simulations. Models trained on past land use data were used to project future land use changes and estimate future changes in potential functional connectivity for 5 different umbrella species. In a second chapter, we integrate these results with the perceived conservation priorities in the region. We conducted a day-long workshop with stakeholders involved in the ongoing connectivity conservation planning effort in the region and collected information on landscape features considered “core” and “linkages” priority areas. We showed the importance of considering land use changes to produce a resilient network of protected areas and highlight the need for a multi-stakeholder approach in the definition of conservation scenarios and the identification of regional priorities.}
